---
title: "Skill set insight and replacement recommendation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Skill insight 
##Load Data
```{r}
setwd("D:/×ÊÁÏ/Columbia/Coursework/Framework 2/Assignment/Own Project/FiFA")
# load three Cluster Data
fifa3_1 = read.csv('3 cluster/fifa_1_Groupcluster.csv')
fifa3_2 = read.csv('3 cluster/fifa_2_Groupcluster.csv')
fifa3_3 = read.csv('3 cluster/fifa_2_Groupcluster.csv')
fifa3 = read.csv('3 cluster/fifa_total_Groupcluster.csv')
#load two cluster data
fifa2_1 =read.csv('2 cluster/fifa_cluster2_1.csv')
fifa2_2 =read.csv('2 cluster/fifa_cluster2_2.csv')
fifa2 = read.csv('2 cluster/fifa_cluster2_total.csv')
fifa = read.csv('fifa_total.csv')
```

##Data Preparation
Select relevant variables to do prediction
```{r}
#Choose related variables
fifa3_1_model <- fifa3_1[,-which(names(fifa3_1)%in%c('ID','Name','Overall','Value','Wage','Real.Face','Jersey.Number','Joined','Contract.Valid.Until','cluster','Position','Release.Clause','International.Reputation'))]
fifa3_2_model <- fifa3_2[,-which(names(fifa3_2)%in%c('ID','Name','Overall','Value','Wage','Real.Face','Jersey.Number','Joined','Contract.Valid.Until','cluster','Position','Release.Clause','International.Reputation'))]
fifa3_3_model <-fifa3_3[,-which(names(fifa3_3)%in%c('ID','Name','Overall','Value','Wage','Real.Face','Jersey.Number','Joined','Contract.Valid.Until','cluster','Position','Release.Clause','International.Reputation'))]
fifa2_1_model <-fifa2_1[,-which(names(fifa2_1)%in%c('ID','Name','Overall','Value','Wage','Real.Face','Jersey.Number','Joined','Contract.Valid.Until','cluster','Position','Release.Clause','International.Reputation'))]
fifa2_2_model <-fifa2_2[,-which(names(fifa2_2)%in%c('ID','Name','Overall','Value','Wage','Real.Face','Jersey.Number','Joined','Contract.Valid.Until','cluster','Position','Release.Clause','International.Reputation'))]
fifa3model <- fifa3[,-which(names(fifa3)%in%c('ID','Name','Overall','Value','Wage','Real.Face','Jersey.Number','Joined','Contract.Valid.Until','cluster','Position','Release.Clause','International.Reputation'))]
fifa2model <- fifa2[,-which(names(fifa2)%in%c('ID','Name','Overall','Value','Wage','Real.Face','Jersey.Number','Joined','Contract.Valid.Until','cluster','Position','Release.Clause','International.Reputation'))]
```
Dummy the PositionGroup variables
```{r}
library(psych)
dummy_position3 <-dummy.code(fifa3$PositionGroup)
dummy_position2 <-dummy.code(fifa2$PositionGroup)
dummy_position3_1 <- dummy.code(fifa3_1_model$PositionGroup)
dummy_position3_2 <-dummy.code(fifa3_2_model$PositionGroup)
dummy_position3_3 <-dummy.code(fifa3_3_model$PositionGroup)
dummy_position2_1 <-dummy.code(fifa2_1_model$PositionGroup)
dummy_position2_2 <-dummy.code(fifa2_2_model$PositionGroup)
```
combine the dummy variables with the original data set
```{r}
fifa3_1_model <-cbind(dummy_position3_1,fifa3_1_model)
fifa3_2_model <-cbind(dummy_position3_2,fifa3_2_model)
fifa3_3_model <-cbind(dummy_position3_3,fifa3_3_model)
fifa2_1_model <-cbind(dummy_position2_1,fifa2_1_model)
fifa2_2_model <-cbind(dummy_position2_2,fifa2_2_model)
fifa3 <-cbind(dummy_position3,fifa3)
fifa2 <-cbind(dummy_position2,fifa2)
```

factor those dummy variables
```{r}
factorcolumn <- function(x){
  x[,which(names(x)%in%c('DEF','FWD','MID','GK'))] <- lapply(x[,which(names(x)%in%c('DEF','FWD','MID','GK'))],as.factor)
  return (x)
}
fifa3_1_model <-factorcolumn(fifa3_1_model)
fifa3_2_model <-factorcolumn(fifa3_2_model)
fifa3_3_model <-factorcolumn(fifa3_3_model)
fifa2_1_model <-factorcolumn(fifa2_1_model)
fifa2_2_model <-factorcolumn(fifa2_2_model)
fifa2 <- factorcolumn(fifa2)
fifa3 <- factorcolumn(fifa3)
```

train-test split
```{r}
#Train-test split use the largest data set as example
# Three clusters dataset 1
set.seed(200)
split3 = sample(1:nrow(fifa3_1_model), nrow(fifa3_1_model)*0.75)
fifa3_1_model_train = fifa3_1_model[split3,]
fifa3_1_model_test = fifa3_1_model[-split3,]
#Three clusters dataset 2
set.seed(200)
split3 = sample(1:nrow(fifa3_2_model), nrow(fifa3_2_model)*0.75)
fifa3_2_model_train = fifa3_2_model[split3,]
fifa3_2_model_test = fifa3_2_model[-split3,]
#Three clusters dataset 3
set.seed(200)
split3 = sample(1:nrow(fifa3_3_model), nrow(fifa3_3_model)*0.75)
fifa3_3_model_train = fifa3_3_model[split3,]
fifa3_3_model_test = fifa3_3_model[-split3,]
#Total
set.seed(200)
split3 = sample(1:nrow(fifa3model), nrow(fifa3model)*0.75)
fifa3_model_train = fifa3model[split3,]
fifa3_model_test = fifa3model[-split3,]

# TWo clusters dataset 1
set.seed(200)
split2 = sample(1:nrow(fifa2_1_model), nrow(fifa2_1_model)*0.75)
fifa2_1_model_train = fifa2_1_model[split3,]
fifa2_1_model_test = fifa2_1_model[-split3,]

# TWo clusters dataset 2
set.seed(200)
split2 = sample(1:nrow(fifa2_2_model), nrow(fifa2_2_model)*0.75)
fifa2_2_model_train = fifa2_2_model[split3,]
fifa3_2_model_test = fifa3_2_model[-split3,]

#Total
set.seed(200)
split2 = sample(1:nrow(fifa2model), nrow(fifa2model)*0.75)
fifa2_model_train = fifa2model[split3,]
fifa2_model_test = fifa2model[-split3,]
```

##Build Random Forest model
```{r}
library(ranger)
#build model
#Three clusters
set.seed(100)
forest3 = ranger(PositionGroup~.-DEF-FWD-MID,data=fifa3_model_train,num.tree = 1000,mtry = 9,classification = True)
#Two clusters
set.seed(100)
forest2 = ranger(PositionGroup~.-DEF-FWD-MID,data=fifa2_model_train,num.tree = 1000,mtry = 9,classification = True)

#predict
#Three Clusters
predForest3 = predict(forest3,data=fifa3_model_test)
#Two Clusters
predForest2 = predict(forest2,data=fifa2_model_test)

#Compare accuracy
#Three Clusters
sum(predForest3$prediction ==fifa3_model_test$PositionGroup)/nrow(fifa3_model_test)
#Two Clusters
sum(predForest2$prediction ==fifa2_model_test$PositionGroup)/nrow(fifa2_model_test)
```

## To unlock which skill sets are important when predicting Position DEF
```{r}
set.seed(100)
rg.forest3<- ranger(PositionGroup~.-DEF-FWD-MID,data=fifa3_model_train, importance = "impurity")
head(sort(rg.forest3$variable.importance,decreasing = TRUE),10)
```

##Draw importance purity plot
```{r}
barplot(head(sort(rg.forest3$variable.importance,decreasing = TRUE),10),cex.names = 0.5)
```

## Draw box plot about position and skill set
SlidingTackle
```{r}
library(dplyr)
library(ggplot2)
fifa2_1 %>%
  filter(PositionGroup != "Unknown") %>%
  ggplot(aes(x= PositionGroup, y=SlidingTackle )) +
  geom_boxplot(fill = "darkgrey") +
  ggtitle("SlidingTackle skill and Position", subtitle = "") 

```

StandingTackle
```{r}
library(ggplot2)
fifa3_1 %>%
  filter(PositionGroup != "Unknown") %>%
  ggplot(aes(x= PositionGroup, y=StandingTackle )) +
  geom_boxplot(fill = "darkgrey") +
  ggtitle("StandingTackle and Position", subtitle = "") 
```

Finishing
```{r}
fifa2_1 %>%
  filter(PositionGroup != "Unknown") %>%
  ggplot(aes(x= PositionGroup, y=Finishing )) +
  geom_boxplot(fill = "darkgrey") +
  ggtitle("Finishing skill and Position", subtitle = "") 
```

Vision
```{r}
fifa3_1 %>%
  filter(PositionGroup != "Unknown") %>%
  ggplot(aes(x= PositionGroup, y=Vision )) +
  geom_boxplot(fill = "darkgrey") +
  ggtitle("Vision and Position", subtitle = "") 
```

Interceptions
```{r}
fifa3_1 %>%
  filter(PositionGroup != "Unknown") %>%
  ggplot(aes(x= PositionGroup, y=Interceptions )) +
  geom_boxplot(fill = "darkgrey") +
  ggtitle("Interceptions and Position", subtitle = "") 
```

HeadingAccuracy
```{r}
fifa3_1 %>%
  filter(PositionGroup != "Unknown") %>%
  ggplot(aes(x= PositionGroup, y=HeadingAccuracy )) +
  geom_boxplot(fill = "darkgrey") +
  ggtitle("HeadingAccuracy and Position", subtitle = "") 
```


#Replacement Recommendation
```{r}
FWD_play <- fifa2[fifa2$FWD == 1,]
DEF_play <- fifa2[fifa2$DEF == 1,]
MID_play <- fifa2[fifa2$MID== 1,]
```

##Build replacment function
Utilize random forest results to build core-skill list 
```{r}
MID_skillset = c('HeadingAccuracy','Vision','LongPassing','SlidingTackle','Finishing','Crossing','RB','LB','ShortPassing','SprintSpeed')
FWD_skillset = c('SlidingTackle','StandingTackle','Interceptions','HeadingAccuracy','Finishing','RB','Marking','LB','LongPassing','CDM')
DEF_skillset = c('SlidingTackle','Finishing','StandingTackle','Vision','RCB','Interceptions','LB','RB','Marking','LCB')
distinctive_skill = c('SlidingTackle','Finishing','RB','LB')
```

put name and ID back to data set
```{r}
fifa2 = cbind(fifa[,c('ID','Name')],fifa2)
```

divide the data set by players' position
```{r}
FWD_play <- fifa2[fifa2$FWD == 1,]
DEF_play <- fifa2[fifa2$DEF == 1,]
MID_play <- fifa2[fifa2$MID== 1,]
```

##Build function
In this fucntion, you can input your targeted player and your budget, and we will find the best player for your team.
```{r}
findsimilarplayer <- function(x,y){
  similarity_list = data.frame()
  if (x %in% FWD_play$ID){
  x<- FWD_play[FWD_play$ID==x,]
    for(row in 1:nrow(FWD_play)){
      i<-FWD_play[row,]
      e<-rbind(i,x)
      f<-dist(e[,FWD_skillset],method = 'euclidean')
      g<-as.matrix(f)
      ID = i$ID
      name = i$Name
      value = i$Value
      similarity_diatance = g[1,2]
      Potential = i$Potential
      similarity_list = rbind(similarity_list,data.frame(ID,name,value,similarity_diatance,Potential)) 
    }
  
  }else if(x %in% DEF_play$ID){
  x<- DEF_play[DEF_play$ID==x,]
    for(row in 1:nrow(DEF_play)){
      i<-DEF_play[row,]
      e<-rbind(i,x)
      f<-dist(e[,DEF_skillset],method = 'euclidean')
      g<-as.matrix(f)
      ID = i$ID
      name = i$Name
      value = i$Value
      similarity_diatance = g[1,2]
      Potential = i$Potential
      similarity_list = rbind(similarity_list,data.frame(ID,name,value,similarity_diatance,Potential)) 
    }
  }else if(x %in% MID_play$ID){
    x<- MID_play[MID_play$ID==x,]
    for(row in 1:nrow(MID_play)){
      i<-MID_play[row,]
      e<-rbind(i,x)
      f<-dist(e[,MID_skillset],method = 'euclidean')
      g<-as.matrix(f)
      ID = i$ID
      name = i$Name
      value = i$Value
      similarity_diatance = g[1,2]
      Potential = i$Potential
      similarity_list = rbind(similarity_list,data.frame(ID,name,value,similarity_diatance,Potential)) 
  }

}
result <- similarity_list[similarity_list$value<y,]
result <- arrange(result,similarity_diatance)
print(head(result))
}
```


Here is the example. We need a player who plays like Messi(ID:158023), but we only have 57000 dollars,which is far lower than Messi's value- 110500 dollars. Who should we buy for our team?
```{r}
findsimilarplayer(158023,57000)
```
It seems like M.Depay is our Guy!












